State of the Practice of Lattice Boltzmann Method Software Development

### 2021-05-20 StateOfPractice/Peter-Notes/Report/Report.tex
1st draft LBM report, tools used

\subsection{Tools Used}

@@

>>>>

\subsection{Tools Used - DONE 1st Draft}
The purpose of tools is to support the development, verification, maintenance, and evolution of software, software processes, and artifacts \citep{ghezzi1991fundamentals}. Many tools are used by current LBM software packages. The tools noted here are subdivided into development tools, dependencies, and project management tools.

\subsubsection{Development Tools}

These tools support the development of end products but do not become part of them, unlike dependencies that remain in the application once it is released \citep{ghezzi1991fundamentals}. The following type of development tools were explicitly noted in the artifacts or web pages of the 23 LBM packages that were assessed. It is likely that other tools, such as debuggers, were used but are not specified here.

\begin{singlespace}
	\begin{multicols}{2}	
		\begin{itemize}
			\item Continuous Integration Tools
			\item Code Editors
			\item Development Environment
			\item Runtime Environments
			\item Compilers
			\item Unit Testing Tools
			\item Correctness Verification Tools
		\end{itemize}
	\end{multicols}
\end{singlespace}

The use of the above tools can verify the correctness of software during its development. Only two of the software packages that were assessed mentioned using continuous integration tools like Travis CI. Code editors and compilers were explicitly noted to have been used by several packages, and were likely used by all of them. One of the packages explicitly noted the use of unit testing, but did not specify the tool that was used. Likewise the use of a tool for verifying the correctness of output was noted by one of the developers. It is likely that similar tools were used when developing other members of the software package list.

\subsubsection{Dependencies}

The following types of dependencies were explicitly noted in the artifacts or web pages of the 23 LBM packages that were assessed. It is possible that other types of dependencies are part of these software packages but are not clearly specified in their artifacts or web sites and because of that they are not listed here.

\begin{singlespace}
	\begin{multicols}{2}	
		\begin{itemize}
			\item Build Automation Tools
			\item Technical Libraries
			\item Domain Specific Libraries
		\end{itemize}
	\end{multicols}
\end{singlespace}

Most of the software packages use some sort of build automation tools, most commonly Make. They also all use various technical and domain specific libraries. Technical libraries include visualization, data analysis, and message passing libraries among others. Domain specific libraries are scientific computing libraries. Specific libraries are not listed here but they fall into the above categories. Libraries that are not explicitly stated in any artifact may fall outside of the categories.

\subsubsection{Project Management Tools}

Many of the software packages that were assessed were developed by teams of two or more people. Their work needed to be coordinated and managed. The following types of project management tools were explicitly noted in the artifacts, web pages, or interviews with the developers of the 23 LBM packages that were assessed. As with development tools and dependencies, it is possible that other types of project management tools were used to coordinate and manage the projects but are not specified and because of that they are not listed here.

\begin{singlespace}
	\begin{multicols}{2}	
		\begin{itemize}
			\item Collaboration Tools
			\item Email
			\item Change Tracking Tools
			\item Version Control Tools
			\item Document Generation Tools
		\end{itemize}
	\end{multicols}
\end{singlespace}

Collaboration tools are noted to have been used when developing the software projects. Most often email and video conferencing is used. Project management software was not explicitly mentioned, but it is possible that some of the project use such software. Many of the projects are located on GitHub, and it's developers use the platform to help manage their projects, especially bug related issues. Most of the projects appear to use change tracking and version control tools. They often use GitHub for this, and a few use Git or CVS. Document generation tools are mentioned in the artifacts of 12 of the projects. Tools such as Sphinx and Doxygen are explicitly used in this capacity. Drasil could be considered as an alternative to generate artifacts since it is geared specifically towards research software domains like LBM software.

@@

- bringing on new developers

- communication of software functionality

- time/funding for documentation

-look at template and interviews

- others
